---
title: "CSE3506 Lab1"
author: "Faraz Suhail"
date: "14/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Name: "Faraz Suhail"
## Reg. No.: "19BCE1525"
## Exercise 1: Regression 

```{r}
#load needed libraries
library(dplyr)

#load the data
df <- read.csv("Lab1.csv")

df = subset(df, select = -c(Gender,Index) )
head(df)
```

```{r}
plot(df, col='blue', main="Relationship between Height and Weight")
```

```{r}
cor(df$Height, df$Weight)
```

### Inference: It is clear from the plot and the correlation that height and weight have a very weak relationship (low correlation)

```{r}
#Fit the model
model = lm(Weight ~ Height, data = df)
summary(model)
```

### Inferences:
1. P value is 0.992 which is not significant as it should be less than 0.05 so model is rejected

2. Multiple R-squared is  1.989e-07 which is very close to 0 so this implies no relation between variables

3. R square has a negative value as the model selected does not follow the trend of the data, therefore leading to a worse fit than the horizontal line.

```{r}
mtcars = subset(mtcars, select = c(mpg,wt) )
head(mtcars)
```

```{r}
plot(mtcars, col='blue', main="Relationship between mpg and wt")
```

```{r}
cor(mtcars$wt, mtcars$mpg)
```

### Inference: It is clear from the plot and the correlation that height and weight have a strong negative relationship (high correlation)

```{r}
#Fit the model
model2 = lm(mpg ~ wt, data = mtcars)
summary(model2)
```

### Inferences:
1. P value is 1.294e-10 which is very significant as it is close to 0 so model is accepted

2. Multiple R-squared is 0.7528 which is close to 1 so this implies strong relationship between variables