---
title: "CSE3506 Lab2"
author: "Faraz Suhail"
date: "21/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Name: "Faraz Suhail"
## Reg. No.: "19BCE1525"
## Exercise 2: Time-series Forecasting

```{r}
library(forecast)
library(tseries)
```
## Arima Model for Gold dataset
```{r}
gold<-read.csv("gold.csv")
gold
```

```{r}
gold_ts<-ts(gold$Price,start = min(gold$Month),end = max(gold$Month),frequency = 1)
par(mar=c(2,2,2,2))
plot(gold_ts)
```

There is upward trend. Time series with trends, or with seasonality, are not stationary

```{r}
acf(gold_ts)
```

The ACF declines gradually from
1 to 0 over a prolonged period of time,
then the series is not stationary

```{r}
pacf(gold_ts)
adf.test(gold_ts)
```

p value high so bad model. 

```{r}
gmodel<-auto.arima(gold_ts,ic="aic",trace=TRUE)
gold_forecast=forecast(gmodel,level = c(95),h=24)
plot(gold_forecast)
```

```{r}
accuracy(gmodel)
```


## Arima Model for GDP dataset
```{r}
gdp=read.csv("gdp.csv")
gdp_ts<-ts(gdp$GDP_gr,start = min(gdp$Year),end = max(gdp$Year),frequency = 1)
par(mar=c(2,2,2,2))
plot(gdp_ts)
```

```{r}
acf(gdp_ts)
```

The ACF falls immediately from 1 to 0,
then equals about 0 thereafter, the series is
stationary

```{r}
pacf(gdp_ts)
adf.test(gdp_ts)
gdp_model<-auto.arima(gdp_ts,ic="aic",trace=TRUE)
gdp_forecast=forecast(gdp_model,level = c(95),h=30)
plot(gdp_forecast)
```

```{r}
accuracy(gdp_model)
```